### 2022-01-19 src-latex/parts/50-xp-setup.tex
Update OCR results with kraken
Updates from Overleaf

\subsubsection{Spacy}
We use the French pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the deep-sequoia and wikiner-fr corpora.
The default NER labels known to the pipeline are PER, ORG, MISC and LOC.
In experiment 1 the base model is fine-tuned on every of the 8 training sets using the same training parameters.
Early stopping is activated with a patience value of 1600 training steps without improvement of the f1 score.

@@

Details can be found for both the SpaCy NER and the CamemBERT NER models in the source code publicly available on the GitHub repository \bertrand{LIEN GITHUB}.

>>>>

\subsubsection{SpaCy}
We use the French pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the deep-sequoia and wikiner-fr corpora.
The default NER labels known to the pipeline are PER, ORG, MISC and LOC.
In experiment 1 the base model is fine-tuned on every of the 8 training sets using the same training parameters.
Early stopping is activated with a patience value of 1600 training steps without improvement of the f1 score.

@@

Details can be found for all models in the source code publicly available on the GitHub repository \bertrand{LIEN GITHUB}.
